### 2023-02-20 Conference Submission/DraftDoc.tex
more edit 2

Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space[citation]. Creating a singular value decomposition of each of our network observations allows us to view the temporal network as a sample, from which we can model the dynamics of edge existence probabilities across time, now a continuous function. Because the progression of the system can now be viewed as a continuous transformation, we can now look to model the change of this system. To regenerate the network from the embedding, we can simply multiply our embedding matrices together. This will give us a random dot product graph, where the entries (i,j) of the matrix will be the probability of an edge from i to j existing[citation]. In this form, the problem can be viewed as a dynamical system We believe this approach will be useful when applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.

>>>>

Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space[citation]. In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continous change in the embedding space. Because the progression of the system can now be viewed as a continuous transformation, we can now look to model the change of this system. To regenerate the network from the embedding, we can simply multiply our embedding matrices together. This will give us a random dot product graph, where the entries (i,j) of the matrix will be the probability of an edge from i to j existing[citation]. In this form, the problem can be viewed as a dynamical system We believe this approach will be useful when applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
